---
title: "assignment4"
author: "Eri"
date: '2023-03-20'
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(factoextra)
library(FactoMineR)
library(gplots)
```

## Data

```{r cars}
data <- read.csv("data.csv",row.names = 1)
```


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
dt <- as.table(as.matrix(data))
# 2. Graph
balloonplot(t(dt), main ="Race vs. Pizza", xlab ="", ylab="",
            label = TRUE, show.margins = FALSE)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r}
# Grand total
n <- sum(data)
# Standardized residuals
chisq <- chisq.test(data)
residuals <- chisq$residuals/sqrt(n)
# Number of dimensions
nb.axes <- min(nrow(residuals)-1, ncol(residuals)-1)
# Singular value decomposition
res.svd <- svd(residuals, nu = nb.axes, nv = nb.axes)
res.svd

sv <- res.svd$d[1:nb.axes] # singular value
u <-res.svd$u
v <- res.svd$v

# Eigenvalues
eig <- sv^2
# Variances in percentage
variance <- eig*100/sum(eig)
# Cumulative variances
cumvar <- cumsum(variance)
eig<- data.frame(eig = eig, variance = variance,
                     cumvariance = cumvar)
head(eig)

barplot(eig[, 2], names.arg=1:nrow(eig), 
       main = "Variances",
       xlab = "Dimensions",
       ylab = "Percentage of variances",
       col ="steelblue")
# Add connected line segments to the plot
lines(x = 1:nrow(eig), eig[, 2], 
      type="b", pch=19, col = "red")
```

```{r}
library(ggpubr)
res.ca = CA(data,graph=F)
fviz_screeplot(res.ca, addlabels = TRUE, ylim = c(0, 100))
```
```{r}
# repel= TRUE to avoid text overlapping (slow if many point)
fviz_ca_biplot(res.ca, repel = TRUE)
```

```{r}
# Contributions of rows to dimension 1
fviz_contrib(res.ca, choice = "row", axes = 1, top = 10)
# Contributions of rows to dimension 2
fviz_contrib(res.ca, choice = "row", axes = 2, top = 10)
# Contributions of rows to dimension 1
fviz_contrib(res.ca, choice = "col", axes = 1, top = 10)
# Contributions of rows to dimension 2
fviz_contrib(res.ca, choice = "col", axes = 2, top = 10)
```


## g.	Find an example in the correspondence plot where the angle between row and column values suggests a strong association – draw the lines from the origin to these two points on the plot.
Strongest association: Angle between Black and Papa Johns

```{r}
fviz_ca_biplot(res.ca, map ="colgreen", arrow = c(T,T),
               repel = TRUE)
```

